R Notebook

### 2019-10-16 src/testing_file.Rmd
looking to add contours

need to add seabed

```{r seabed files}
slst <- list.files("../data/env/ascii/ascii2010", pattern = "temp", full.names = TRUE)
sr <- raster(slst[1])
plot(sr)
```

@@

>>>>

@@

# add seabed?
need to add seabed

```{r seabed files}
contwgs <- shapefile("../data/env/contours_50m.shp") #created in arcgis from glorys bottomdepth using 3d licence contour tool
plot(contwgs)
aea <- raster("../output/env/aea.tif") #the correct CRS
corcrs <- aea@crs
contaea <- raster::reproject(contwgs, aea)
